Paper 2, Econ 980x

### 2022-12-12 Paper2.Rmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
library(tinytex)
library(ipumsr)

@@

@@

#leisure hours aggregate by gender
csv %>%
  group_by(gender) %>%
  ggplot(mapping = aes(x = bls_leis) )+
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender) +
    labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

@@

# Median
csv %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Median 
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Mean
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = mean_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Mean daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# All Quantile
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
    facet_wrap(~ gender) +
  labs(
  title = "Daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
  facet_wrap(~gender) +
    labs(
  title = "Daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

@@

g <- csv %>%
  lm(formula = bls_leis ~ gender)

@@

y <- csv %>%
  lm(formula = bls_leis ~ gender + year)

@@

newcsv
newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race)

# 
a <- newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race) 
summary(a)

@@

b <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ) 
summary(b)

@@

c <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild) 
summary(c)

@@

d <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild + marst_simple) 
summary(d)

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```
```{r employment}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
library(tinytex)
library(ipumsr)
library(dplyr)
library(haven)
library(survey)
library(spatstat)

@@

view(c)
```

@@

#leisure hours aggregate by gender
csv %>%
  filter(year < 2020) %>%
  group_by(gender) %>%
  ggplot(mapping = aes(x = bls_leis) )+
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender) +
    labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

@@

# Median
csv %>%
  filter(year < 2020) %>%
  group_by(gender, year) %>%
  summarize(median_leisure = weighted.median(bls_leis, as.numeric(wt06), na.rm=TRUE)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_leisure)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# mean
csv %>%
  filter(year < 2020) %>%
  group_by(gender,year) %>%
  summarize(new = weighted.mean(bls_leis, wt06)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = new)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Weighted mean daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Median 
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(median_bls_leis = weighted.median(bls_leis, wt06)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Weighted median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Mean
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(mean_bls_leis = weighted.mean(bls_leis, wt06)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = mean_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Mean daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# All Quantile
csv %>%
  filter(year < 2020) %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = weighted.quantile(bls_leis, wt06, prob = 0.25), quantile_50 = weighted.quantile(bls_leis, wt06, prob = 0.50), quantile_75 = weighted.quantile(bls_leis, wt06, prob = 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
    facet_wrap(~ gender) +
  labs(
  title = "Weighted daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# by year, gender
csv %>%
  filter(year < 2020) %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = weighted.quantile(bls_leis, wt06, prob = 0.25), quantile_50 = weighted.quantile(bls_leis, wt06, prob = 0.50), quantile_75 = weighted.quantile(bls_leis, wt06, prob = 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
  facet_wrap(~gender) +
    labs(
  title = "Weighted daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

@@

g <- csv %>%
  lm(formula = bls_leis ~ gender, weight = wt06)
summary(g)

@@

y <- csv %>%
  lm(formula = bls_leis ~ gender + year, weight = wt06)

@@

newcsv
newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race, weight = wt06)

# 
a <- newcsv %>%
  lm(formula = bls_leis ~ gender + year + age + race, weight = wt06) 
summary(a)

@@

b <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ, weight = wt06) 
summary(b)

@@

c <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild, weight = wt06) 
summary(c)

@@

d <- newcsv1 %>%
  lm(formula = bls_leis ~ gender + year + age + race + new_educ + nchild + marst_simple, weight = wt06) 
summary(d)

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```

```{r employment}
